Dissertation Manuscript

### 2023-10-16 paper.qmd
render again

  <a class="btn btn-danger btn-sm mb-1" target="_blank" href="/manuscript/output/Full_Dissertation-nice.pdf">
  <iconify-icon inline="" icon="fa6-solid:file-arrow-down"></iconify-icon> &ensp;PDF <small>(download)</small>
  </a>

>>>>

   <a class="btn btn-warning btn-sm mb-1" href="/manuscript/manuscript.pdf.md" target="manuscript">
  <iconify-icon inline="" icon="fa6-solid:file-pdf"></iconify-icon> &ensp;Manuscript-md
  </a>
